---
title: "Kat Data Thinger"
author: "Alan Nielsen"
date: "February 3, 2019"
output: html_document
---

```{r setup}
library(data.table)
library(tidyverse)
library(ggthemes)

setwd("C:/Users/Alan/Documents/GitHub/Stekic-et-al/Data/50s/")
files50  <- list.files(pattern = '\\.csv')
tables50 <- lapply(files50, read.csv, header = TRUE)
combined.df.50 <- do.call(rbind , tables50)

combined.df.50[] <- lapply(combined.df.50, function(x) gsub("\\\\", "", x))

setwd("C:/Users/Alan/Documents/GitHub/Stekic-et-al/Data/40s/")
files40  <- list.files(pattern = '\\.csv')
tables40 <- lapply(files40, read.csv, header = TRUE)
combined.df.40 <- do.call(rbind , tables40)

colnames(combined.df.50)<- c("rtD", "key_press", "trialtype2", "TrialIndex", "elapsed", "node_id", "viewhist", "responses", "Yoking", "RT", "RespKey", "RespCorr", "TrialType", "Image", "Label", "Location", "CorrectResponse", "Block", "BlockTrial", "Condition", "LabelType", "Subcondition", "TrialNum")


colnames(combined.df.40)<- c("rtD", "key_press", "trialtype2", "TrialIndex", "elapsed", "node_id", "viewhist", "responses", "Yoking", "RT", "RespKey", "RespCorr", "TrialType", "Image", "Label", "Location", "CorrectResponse", "Block", "BlockTrial", "Condition", "LabelType", "Subcondition", "TrialNum")
  
combined.df <- rbind(combined.df.50, combined.df.40)

head(combined.df)

```


So that's the data all combined, but now it has to be cleaned up considerably

1) remove all of the slashes and backslashes everywhere to have data that we can actually read and parse properly with later commands
2) Extract the biological data from the participants, which is on line 4 of each participant's dataframe, then put it back into the main dataframe as the Age and Gender columns
3) Add a unique participantID column (from the filenames)
4) Trim down to the required columns and re-order them
5) Delete the useless rows
6) Make sure the columns are all the right data types
7) Delete Wonky data- participant 7gtriiTixvBaQ has some impossible values- something went wrong during that run of the experiment


```{r cleaning up the data}
#1
combined.df[] <- lapply(combined.df, function(x) gsub("\\\\", "", x))
combined.df[] <- lapply(combined.df, function(x) gsub("[{}]", "", x))
combined.df[] <- lapply(combined.df, function(x) gsub("\"", "", x))

#2
biodata <- combined.df[seq(4, nrow(combined.df), 246),]
biodata <- as.data.frame(biodata$responses)
colnames(biodata) <- "biodata"

biodata <- separate(biodata, col=biodata, into = c("Age", "Gender", "Specify"), sep = ",")

biodata$Age <- sub("age:", "", biodata$Age)
biodata$Gender <- sub("gender:", "", biodata$Gender)
biodata$Specify <- sub("specify:", "", biodata$Specify)

combined.df$Age <- rep(biodata$Age, each = 246)
combined.df$Gender <- rep(biodata$Gender, each = 246)

#3
files <- c(files40, files50)
files <- sub(".csv", "", files)

combined.df$ParticipantID <- rep(files, each= 246)

#4
AggregatedData <- subset(combined.df, select = c("ParticipantID", "Condition", "Subcondition", "Yoking", "TrialNum", "TrialType", "Block", "BlockTrial", "Image", "Label", "Location", "CorrectResponse", "RespKey", "RespCorr", "RT"))

#5
AggregatedData <- subset(AggregatedData, TrialNum > 0)

#6
AggregatedData$ParticipantID <- as.factor(AggregatedData$ParticipantID)
AggregatedData$Condition <- as.factor(AggregatedData$Condition)
AggregatedData$Subcondition <- as.factor(AggregatedData$Subcondition)
AggregatedData$Yoking <- as.factor(AggregatedData$Yoking)
AggregatedData$TrialType <- as.factor(AggregatedData$TrialType)
AggregatedData$Location <- as.factor(AggregatedData$Location)

AggregatedData$TrialNum <- as.numeric(AggregatedData$TrialNum)
AggregatedData$Block <- as.numeric(AggregatedData$Block)
AggregatedData$BlockTrial <- as.numeric(AggregatedData$BlockTrial)
AggregatedData$RespCorr <- as.numeric(AggregatedData$RespCorr)
AggregatedData$RT <- as.numeric(AggregatedData$RT)


#7
AggregatedData <- subset(AggregatedData, ParticipantID != "7gtriiTixvBaQ")


```


Now we need to output some data for kat, who wants a subset of participants from conditions 1, 2, 3A, and 3B

```{r Data For Kat}

SubData <- subset(AggregatedData, Condition == 1|Condition == 2| Condition == "3A"|Condition == "3B"|Condition == 10)

write.csv(SubData, file=("C:/Users/Alan/Documents/GitHub/Stekic-et-al/Data/KatSample.csv"))

```


Now we can aggregate and look at some summary data/graphs to get some idea what is going on in our conditions etc.

For this, we're going to aggregate data across subjects for the interaction of Trial Type x Block within subjects and condition between subjects

We're also going to collapse 3A and 3B and 6A and 6B

We're also goign to collapse all the "arbitrary" conditions 7-9 as they look pretty similar across the board

```{r Aggregating Data for Analyses and Graphs, warning= FALSE}

AggData <- aggregate(RespCorr ~ Condition + TrialType + Block, data=AggregatedData, mean)
AggData$Block <- as.factor(AggData$Block)

AggData$TrialType <- factor(AggData$TrialType, level = c ("Training", "Testing"))

AggData$Condition <- sub("A", "", AggData$Condition)
AggData$Condition <- sub("B", "", AggData$Condition)
AggData$Condition <- sub("8", "7", AggData$Condition)
AggData$Condition <- sub("9", "7", AggData$Condition)



AggData$Condition <- factor(AggData$Condition,
                            level= c("1", "2", "3", "4", "5", "6", "7", "10"),
                            labels = c("Iconic Category", "Counter-Iconic Category", "Conventional Category",
                                       "Systematic Iconic", "Systematic Counter-Iconic", "Systematic Conventional",
                                       "Arbitrary",
                                       "No Label"))

ggplot(data=AggData, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition, 
                                                             linetype = Condition)) +
  scale_linetype_manual(values = c("solid", "solid", "solid",
                          "longdash", "longdash", "longdash", "dotdash",
                          "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#0066CC", "#CC0033","#33FF00", "#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  theme_tufte()


AggDataRT <- aggregate(RT ~ Condition + TrialType + Block, data=AggregatedData, mean)
AggDataRT$Block <- as.factor(AggData$Block)

AggDataRT$TrialType <- factor(AggDataRT$TrialType, level = c ("Training", "Testing"))

AggDataRT$Condition <- sub("A", "", AggDataRT$Condition)
AggDataRT$Condition <- sub("B", "", AggDataRT$Condition)
AggDataRT$Condition <- sub("8", "7", AggDataRT$Condition)
AggDataRT$Condition <- sub("9", "7", AggDataRT$Condition)



AggDataRT$Condition <- factor(AggDataRT$Condition,
                            level= c("1", "2", "3", "4", "5", "6", "7", "10"),
                            labels = c("Iconic Category", "Counter-Iconic Category", "Conventional Category",
                                       "Systematic Iconic", "Systematic Counter-Iconic", "Systematic Conventional",
                                       "Arbitrary",
                                       "No Label"))

ggplot(data=AggDataRT, aes(x=Block, y=RT, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_line(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition, 
                                                             linetype = Condition)) +
  scale_linetype_manual(values = c("solid", "solid", "solid",
                          "longdash", "longdash", "longdash", "dotdash",
                          "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#0066CC", "#CC0033","#33FF00", "#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  theme_tufte()
  

```


So there are definitely some fucky values for response times- one notable one is a response time of -3595188 milliseconds (negative 35,951 seconds, or approximately -10 hours... don't know how that happens) which is why you see the *huge* dip above for Block 4 of Condition 4- it's such a huge value it drags the whole things down

But there is also a really big rrange of overall response times

It turns out, in fact, that there is such a broad range of Response Tiems that we can't sensibly plot a histograph ro density plot, so lets throw out some of that data

```{r Cleaning up RT data}

library(outliers)
plot(density(AggregatedData$RT))

#Remove Negative RTs, which are technically impossible (and its curious how they are being recorded as such)
AggregatedDataTrim <- subset(AggregatedData, RT > 0)
plot(density(AggregatedDataTrim$RT))

#So that doesn't work great, because there are still extreme positive values- up to 2460568 ms
#There are principled ways to make a cutoff, but I think we want to start wtih dropping trials that take over 30 seconds
AggregatedDataTrim <- subset(AggregatedDataTrim, RT<30000)
plot(density(AggregatedDataTrim$RT))

#That gives us something nicer, but we can see the tail is pretty much gone at around 10 seconds, so for the cleanest data to look at let's cut things off there

AggregatedDataTrim <- subset(AggregatedDataTrim, RT<10000)
plot(density(AggregatedDataTrim$RT))

#Now we can plot our RT data without it looking totally wonky

AggDataRT2 <- aggregate(RT ~ Condition + TrialType + Block, data=AggregatedDataTrim, mean)
AggDataRT2$Block <- as.factor(AggDataRT2$Block)

AggDataRT2$TrialType <- factor(AggDataRT2$TrialType, level = c ("Training", "Testing"))

AggDataRT2$Condition <- sub("A", "", AggDataRT2$Condition)
AggDataRT2$Condition <- sub("B", "", AggDataRT2$Condition)
AggDataRT2$Condition <- sub("8", "7", AggDataRT2$Condition)
AggDataRT2$Condition <- sub("9", "7", AggDataRT2$Condition)



AggDataRT2$Condition <- factor(AggDataRT2$Condition,
                            level= c("1", "2", "3", "4", "5", "6", "7", "10"),
                            labels = c("Iconic Category", "Counter-Iconic Category", "Conventional Category",
                                       "Systematic Iconic", "Systematic Counter-Iconic", "Systematic Conventional",
                                       "Arbitrary",
                                       "No Label"))

ggplot(data=AggDataRT2, aes(x=Block, y=RT, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition, 
                                                             linetype = Condition)) +
  scale_linetype_manual(values = c("solid", "solid", "solid",
                          "longdash", "longdash", "longdash", "dotdash",
                          "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#0066CC", "#CC0033","#33FF00", "#33FF00", "#000000")) +
  labs(x="Block", y="Response Time") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  theme_tufte()

```



Kat wants some plots just for conditions 1-3 and 10, so lets do those

```{r Kat Plots, warning= FALSE}

AggregatedDataKat <- AggregatedDataTrim
AggregatedDataKat$Condition <- sub("A", "", AggregatedDataKat$Condition)
AggregatedDataKat$Condition <- sub("B", "", AggregatedDataKat$Condition)

AggregatedDataKat$Condition <- as.factor(AggregatedDataKat$Condition)

SubDataKat <- subset(AggregatedDataKat, Condition == 1|Condition == 2| Condition == 3|Condition == 10)

AggDataKatCorr <- aggregate(RespCorr ~ Condition + TrialType + Block, data= SubDataKat, mean)
AggDataKatRT <- aggregate(RT ~ Condition + TrialType + Block, data= SubDataKat, mean)


AggDataKatCorr$Block <- as.factor(AggDataKatCorr$Block)

AggDataKatCorr$TrialType <- factor(AggDataKatCorr$TrialType, level = c ("Training", "Testing"))

AggDataKatCorr$Condition <- factor(AggDataKatCorr$Condition,
                            level= c("1", "2", "3", "10"),
                            labels = c("Iconic Category", "Counter-Iconic Category", "Conventional Category",
                                       "No Label"))

ggplot(data=AggDataKatCorr, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition, 
                                                             linetype = Condition)) +
  scale_linetype_manual(values = c("solid", "solid", "solid",
                          "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  theme_tufte()

AggDataKatRT$Block <- as.factor(AggDataKatRT$Block)

AggDataKatRT$TrialType <- factor(AggDataKatRT$TrialType, level = c ("Training", "Testing"))

AggDataKatRT$Condition <- factor(AggDataKatRT$Condition,
                            level= c("1", "2", "3", "10"),
                            labels = c("Iconic Category", "Counter-Iconic Category", "Conventional Category",
                                       "No Label"))

ggplot(data=AggDataKatRT, aes(x=Block, y=RT, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition, 
                                                             linetype = Condition)) +
  scale_linetype_manual(values = c("solid", "solid", "solid",
                          "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Average Response Time") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType, scales="free", space= "free_x") +
  theme_tufte()


```


So, these are super interesting, but we also want to look at generalisation - in the testing trials participants are introduced to novel exemplars of the categories- what we really need to know is how well they perform on these new stimuli

Unfortunately, we're dumb and didn't encode that anywhere in the stimlist files, so we need to write some code to figure out, for each participant, what images are new and what images are not

```{r Novel Exemplars}

participantIDs <- unique(AggregatedData$ParticipantID)
participantdata <- list()
participantdata.training <- list()
participantdata.testing <- list()

testingtrials <- list()
trainingtrials <- list()


for (participant in participantIDs) {
  
  participantdata <- subset(AggregatedData, ParticipantID == participant)
  participantdata.training <- subset(participantdata, TrialType == "Training")
  participantdata.testing <- subset(participantdata, TrialType == "Testing")
  
  
  TrainingFigures <- unique(participantdata.training$Image)
  
  participantdata.training$Generalisation <- NA
  
  participantdata.testing$Generalisation <- ifelse(
    participantdata.testing$Image %in% TrainingFigures,
    "Old",
    "New")
  
  trainingtrials <- rbind(trainingtrials, participantdata.training)
  testingtrials <- rbind(testingtrials, participantdata.testing)
  
  
}

AggregatedData2 <- rbind(trainingtrials, testingtrials)

```

Okay that's that calculated, now we just need to do all of the other manipulations of excluding response times etc to take a look at some relatively cleaner data

```{r A second look, warning= FALSE}

AggregatedData2$Block <- as.factor(AggregatedData2$Block)
AggregatedData2$TrialType <- factor(AggregatedData2$TrialType, level = c ("Training", "Testing"))
AggregatedData2$TrialType2 <- paste(AggregatedData2$TrialType, AggregatedData2$Generalisation, sep = "-")
AggregatedData2$Generalisation <- as.factor(AggregatedData2$Generalisation)

AggregatedData2$TrialType2 <- factor(AggregatedData2$TrialType2, level = c ("Training-NA", "Testing-Old", "Testing-New"),
                                     labels = c("Training", "Testing-Old", "Testing-New"))

AggregatedData2$Condition <- sub("A", "", AggregatedData2$Condition)
AggregatedData2$Condition <- sub("B", "", AggregatedData2$Condition)
AggregatedData2$Condition <- sub("8", "7", AggregatedData2$Condition)
AggregatedData2$Condition <- sub("9", "7", AggregatedData2$Condition)

AggregatedData2$Condition <- factor(AggregatedData2$Condition,
                            levels= c("1", "2", "3", "4", "5", "6", "7", "10"),
                            labels = c("Iconic Category", "Counter-Iconic Category", "Conventional Category",
                                       "Systematic Iconic", "Systematic Counter-Iconic", "Systematic Conventional",
                                       "Arbitrary",
                                       "No Label"))

#Trim out weird RTs
AggregatedData2 <- subset(AggregatedData2, RT > 0)
AggregatedData2 <- subset(AggregatedData2, RT < 10000)



AggData2 <- aggregate(RespCorr ~ Condition + TrialType + Block + TrialType2 , data=AggregatedData2, mean, na.rm= FALSE)


ggplot(data=AggData2, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition, 
                                                             linetype = TrialType2)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#0066CC", "#CC0033","#33FF00", "#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()



```



So now lets look just at the data that kat wants

```{r Cleaned up katdata, warning = FALSE}

KatData2 <- subset(AggregatedData2, Condition == "Iconic Category"|Condition == "Counter-Iconic Category"| Condition == "Conventional Category"|Condition == "No Label")

KatDataAgg2 <- aggregate(RespCorr ~ Condition + TrialType + Block + TrialType2 , data=KatData2, mean)

ggplot(data=KatDataAgg2, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()

KatDataAgg2RT <- aggregate(RT ~ Condition + TrialType + Block + TrialType2 , data=KatData2, mean)

ggplot(data=KatDataAgg2RT, aes(x=Block, y=RT, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= FALSE, aes(colour = Condition)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Average Response Time") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()



```




Finally lets take a look at this cleaned up data wiht some of the deviation plotted, which means we need to aggregated within participants, rather than between them

```{r data with variance, warning = FALSE}

KatDataAgg3 <- aggregate(RespCorr ~ ParticipantID + Condition + TrialType + Block + TrialType2 , data=KatData2, mean)

ggplot(data=KatDataAgg3, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=0.5, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= TRUE, aes(colour = Condition)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()

KatDataAgg3RT <- aggregate(RT ~ ParticipantID + Condition + TrialType + Block + TrialType2 , data=KatData2, mean)

ggplot(data=KatDataAgg3RT, aes(x=Block, y=RT, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= TRUE, aes(colour = Condition)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#000000")) +
  labs(x="Block", y="Average Response Time") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()

```



Lets take a look just at our arbitrary conditions (conditions 7-9) to see if we can justify collapsing them

```{r Data Tidying 2}

#Cut out outlier trials for RT
library(outliers)
plot(density(AggregatedData$RT))

AggregatedDataTrim <- subset(AggregatedData, RT > 0)
plot(density(AggregatedDataTrim$RT))
AggregatedDataTrim <- subset(AggregatedDataTrim, RT<30000)
plot(density(AggregatedDataTrim$RT))
AggregatedDataTrim <- subset(AggregatedDataTrim, RT<10000)
plot(density(AggregatedDataTrim$RT))

#Add generalisation information
participantIDs <- unique(AggregatedDataTrim$ParticipantID)
participantdata <- list()
participantdata.training <- list()
participantdata.testing <- list()

testingtrials <- list()
trainingtrials <- list()


for (participant in participantIDs) {
  
  participantdata <- subset(AggregatedDataTrim, ParticipantID == participant)
  participantdata.training <- subset(participantdata, TrialType == "Training")
  participantdata.testing <- subset(participantdata, TrialType == "Testing")
  
  
  TrainingFigures <- unique(participantdata.training$Image)
  
  participantdata.training$Generalisation <- NA
  
  participantdata.testing$Generalisation <- ifelse(
    participantdata.testing$Image %in% TrainingFigures,
    "Old",
    "New")
  
  trainingtrials <- rbind(trainingtrials, participantdata.training)
  testingtrials <- rbind(testingtrials, participantdata.testing)
  
  
}

AggregatedData2 <- rbind(trainingtrials, testingtrials)


#Factor levels, adding Trial Type 2

AggregatedData2$Block <- as.factor(AggregatedData2$Block)
AggregatedData2$TrialType <- factor(AggregatedData2$TrialType, level = c ("Training", "Testing"))
AggregatedData2$TrialType2 <- paste(AggregatedData2$TrialType, AggregatedData2$Generalisation, sep = "-")
AggregatedData2$Generalisation <- as.factor(AggregatedData2$Generalisation)

AggregatedData2$TrialType2 <- factor(AggregatedData2$TrialType2, level = c ("Training-NA", "Testing-Old", "Testing-New"),
                                     labels = c("Training", "Testing-Old", "Testing-New"))

```


```{r Looking at Arbitrary Data, warning = FALSE}
#Subset to just Arbitrary Data
ArbData <- subset(AggregatedData2, Condition== 7|Condition == 8|Condition ==9)

ArbDataAgg<- aggregate(RespCorr ~ ParticipantID + Condition + TrialType + Block + TrialType2 , data=ArbData, mean)
ArbDataAgg$Condition <- factor(ArbDataAgg$Condition)

#Most basic model
library(lme4)
library(lmerTest)
ArbData.Model1 <- lmer(RespCorr ~ Condition * Block * TrialType2 + (1|ParticipantID), data=ArbDataAgg)
summary(ArbData.Model1)

#use step to simplify model

stepFirst <- step(ArbData.Model1)
ArbData.Model2 <- get_model(stepFirst)
summary(ArbData.Model2)

#These models show no effect of Condition - so we can indeed aggregate all of our arbitrary conditions 7 8 and 9 for subsequent analyses
#To show that clearly, lets graph them quickly
ggplot(data=ArbDataAgg, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=0.5, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= TRUE, aes(colour = Condition)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()

#We should also verify whether this is true for Response Times

ArbDataRTAgg<- aggregate(RT ~ ParticipantID + Condition + TrialType + Block + TrialType2 , data=ArbData, mean)
ArbDataRTAgg$Condition <- factor(ArbDataAgg$Condition)

ArbData.ModelRT1 <- lmer(RT ~ Condition * Block * TrialType2 + (1|ParticipantID), data=ArbDataRTAgg)
summary(ArbData.ModelRT1)

stepFirstRT <- step(ArbData.ModelRT1)
ArbData.ModelRT2 <- get_model(stepFirstRT)
summary(ArbData.ModelRT2)

#So for RT we get an effect of condition, but stepwise model selection eliminates this effect

ggplot(data=ArbDataRTAgg, aes(x=Block, y=RT, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=1.75, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= TRUE, aes(colour = Condition)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00")) +
  labs(x="Block", y="Average Response Time") +
  #scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()


```



So, the above demonstrates that we can collapse our arbitrary conditions- there doesn't seem to be much interesting going on between conditions

```{r Collapsing Arbitrary Conditions}

AggregatedData3.ArbColl <- AggregatedData2

#Coding all arbitrary conditions as condition 7
AggregatedData3.ArbColl$Condition <- sub("8", "7", AggregatedData3.ArbColl$Condition)
AggregatedData3.ArbColl$Condition <- sub("9", "7", AggregatedData3.ArbColl$Condition)


```

The other main groups to try to collapse are 3A vs. 3B and 6A vs. 6B- lets quickly output those as a graph and see what we have going on

```{r 3A vs 3B, 6A vs 6B graphs, warning = FALSE}

AggregatedData4.3AB6AB <- subset(AggregatedData3.ArbColl, Condition == "3A"|Condition == "3B"|Condition == "6A"|Condition == "6B")

AggregatedData4.3AB6AB$Condition <- factor(AggregatedData4.3AB6AB$Condition)

ABAgg<- aggregate(RespCorr ~ ParticipantID + Condition + TrialType + Block + TrialType2 , data=AggregatedData4.3AB6AB, mean)
ABAggRT<- aggregate(RT ~ ParticipantID + Condition + TrialType + Block + TrialType2 , data=AggregatedData4.3AB6AB, mean)

#Basic Model
ABData.Model1 <- lmer(RespCorr ~ Condition * Block * TrialType2 + (1|ParticipantID), data=ABAgg)
summary(ABData.Model1)

#use step to simplify model

stepFirst <- step(ABData.Model1)
ABData.Model2 <- get_model(stepFirst)
summary(ABData.Model2)


```

There are still some differences between the conditions here - lets see if they are because of differences between 3 and 6 conditions generally or A/B subconditions

```{r Graphing AB, warning = FALSE}

#This may be easy enough to spot in a graph- so lets take a look
ggplot(data=ABAgg, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=0.5, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= TRUE, aes(colour = Condition)) +
 # scale_linetype_manual(values = c("solid", "solid", "solid",
  #                        "longdash", "longdash", "longdash", "dotdash",
  #                        "dotted")) +
 # scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00",)) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()

```

It doesn't seem super clear, from looking at the graphs, what is going on here- for training trials 3A and 3B look identical, as do 6A and 6B, but for testing trials both new and old the "B" conditions seem to sit on top of the "A" conditions

It's not necessarily clear what that would mean, but I can't particularly think of an explanation for that data. To rehearse, the A vs. B difference is simply which set of conventional labels is assigned to jagged vs. curvy images - so really we'd expect if there were differences that they would show up in the earliest learning trials- the fact that they show up in testing trials but not training trials is hard to explain, so for now we'll leave it and collapse these as well

```{r Collapsing AB}
AggregatedData5.ABColl <- AggregatedData3.ArbColl

AggregatedData5.ABColl$Condition <- sub("A", "", AggregatedData5.ABColl$Condition)
AggregatedData5.ABColl$Condition <- sub("B", "", AggregatedData5.ABColl$Condition)
AggregatedData5.ABColl$Condition <- factor(AggregatedData5.ABColl$Condition)

```

So now we can start to look at something more like a complete model, which we'll first do including "Condition" as a variable of its own (rather than as a crossing of other variables)

```{r first look full data, warning=FALSE}
#Relevel and rename the condition factor
AggregatedData5.ABColl$Condition <- factor(AggregatedData5.ABColl$Condition,
                            level= c("1", "2", "3", "4", "5", "6", "7", "10"),
                            labels = c("Iconic Category", "Counter-Iconic Category", "Conventional Category",
                                       "Systematic Iconic", "Systematic Counter-Iconic", "Systematic Conventional",
                                       "Arbitrary",
                                       "No Label"))

TrimAgg<- aggregate(RespCorr ~ ParticipantID + Condition + Subcondition + TrialType + Block + TrialType2 , data=AggregatedData5.ABColl, mean)
TrimRTAgg <- aggregate(RT ~ ParticipantID + Condition +Subcondition+  TrialType + Block + TrialType2 , data=AggregatedData5.ABColl, mean)



ggplot(data=TrimAgg, aes(x=Block, y=RespCorr, group=Condition)) +
  #geom_line(color="#aa0022", size=1.75) +
  #geom_point(size=0.5, aes(colour = Condition)) +
  geom_smooth(method='loess', formula= y ~ x, se= TRUE, aes(colour = Condition, linetype= Condition)) +
  scale_linetype_manual(values = c("solid", "solid", "solid",
                      "longdash", "longdash", "longdash", "dotdash",
                      "dotted")) +
  scale_color_manual(values= c("#0066CC", "#CC0033","#33FF00", "#0066CC", "#CC0033","#33FF00", "#33FF00", "#000000")) +
  labs(x="Block", y="Proportion of Correct Responses") +
  scale_y_continuous(limits = c(0.45,1), breaks=c(0.5,0.6,0.7,0.8,0.9,1.0)) +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme_tufte()

```

```{r First FUll Model}
#Basic Model
TrimAgg$Block <- as.numeric(as.character(TrimAgg$Block))

TrimData.Model1 <- lmer(RespCorr ~ Condition *Subcondition * Block * TrialType2 + (1|ParticipantID), data=TrimAgg)
summary(TrimData.Model1)

#use step to simplify model

stepFirst <- step(TrimData.Model1)
TrimData.Model2 <- get_model(stepFirst)
summary(TrimData.Model2)


```

SO there are definitely some differences that are pretty substantial, and some that get washed out by the step function, as well as some pretty surprising bits, like the fact that there deosn't seem to be a main effect of trial type where on test trials new items are harder than old items

The results as they are shown also don't give us very much to go by for the post-hoc comparisons of which specific conditions are better than eaach other. Those are obviously things that we can get at, but are probably not worth getting at with a rough-and-ready approach

So instead lets try to break this down such that we can see main effects of systematicity, for example, rather than the conditions, which are of course themselves interactions of the effects we're interested in

```{r Reclassifying Data}

#We'er going to add some columns for our factors
TrimAgg2 <-  TrimAgg
library(plyr)
library(dplyr)

#Category vs Individual
TrimAgg2$CatvInd <- mapvalues(TrimAgg2$Condition,
                              from= unique(TrimAgg2$Condition),
                              to= c(rep("Category", 3), rep("Individual", 4), "None")
                              )

#Systematic vs Non
TrimAgg2$SysvArb <- mapvalues(TrimAgg2$Condition,
                              from= unique(TrimAgg2$Condition),
                              to= c(rep("Category2", 3), rep("Systematic", 3), "Non-Systematic", "None2")
                              )

#Iconicity
TrimAgg2$Iconicity <- mapvalues(TrimAgg2$Condition,
                              from= unique(TrimAgg2$Condition),
                              to= c("Iconic", "Counter-Iconic", "Conventional", "Iconic", "Counter-Iconic", "Conventional","Arbitrary", "None3")
                              )

#And now pop out a new model
#So here for this model we're going to pop out subcondition (whether they approach or retreat from Jagged and Curved respectively) and Condition (replaced with our new partially crossed factors)

#I also added in "family = binomial" because I've forgotten to do that up until now (this also means moving to using "glmer" from afex)

afex.noInt <- mixed(RespCorr ~ CatvInd + SysvArb + Iconicity+  Block + TrialType2 + (1|ParticipantID),
                         data=TrimAgg2,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa"),
                         method = 'LRT',
                         progress=FALSE)


afex.noInt$anova_table


```

So a basic model with no interactions is definitely pretty crappy- it looks good- some significant main effects, but when we look at the ChiSquared values of 0 that's a pretty good indication that something is going wrong

We get even grosser results when we include our interactions - note the below model is tagged include= FALSE because it takes a whole day to run and doesn't in any way converge
```{r Interaction model, include= FALSE}


afex.full <- mixed(RespCorr ~ CatvInd * SysvArb * Iconicity *  Block * TrialType2 + (1|ParticipantID),
                         data=TrimAgg2,
                         family=binomial,
                         control=glmerControl(optimizer="bobyqa"),
                         method = 'LRT',
                         progress=FALSE)


afex.full$anova_table

```

# Tackling our Data one step at a time

The above sections have a number of errors, including the fact that we're trying to conduct binomial LMER on aggregated data, which is actually a no-no



