---
title: "Pilot Data for Master Thesis"
output: 
  html_document:
    keep_md: true
    theme: journal
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
    code_folding: hide
---
#Pilot data exploration

####Loading Libraries
```{r}
library(data.table)
library(tidyverse)
library(ggthemes)
library(outliers)
library(lme4)
library(lmerTest)
library(afex)
library(kableExtra)
library(agricolae)
library(multcomp)
library(devtools)
```

####Plotting Correctness through Trial type (it works with CleanData4!!!)
```{r}

DataNew <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "10"| Condition == "9")

DataSubset$TrialType2 = factor(DataSubset$TrialType2, levels=c("Training","Testing-Old","Testing-New"), labels=c("Training","Testing-Old","Testing-New")) 

ggplot(DataSubset, aes(x= Block, y= RespCorr, colour= Condition, linetype = Condition)) + 
  geom_smooth(aes(colour = Condition),size = 1.0,se = TRUE, method= 'loess', formula =  y~x)+
  
  scale_linetype_manual(values = c("solid", "dotdash",
                                    "solid", "dotdash",
                                    "longdash")) +
  
  scale_color_manual(values= c("#0066CC", "#000000",
                               "#33FF00", "#33FF00", 
                                "#CC0033")) +
                               
  ggtitle("Performance by Block") +
  labs(x="Block", y="Proportion of Correctness") +
  facet_grid(~TrialType2, scales="free", space= "free_x" ) +
  theme(axis.title.y = element_text(size=12,  color="#666666")) +
  theme(axis.text = element_text(size=8)) +
  theme(plot.title = element_text(size=16, face="bold", hjust=0, color="#666666")) +
  theme(strip.text.x = element_text(size = 8, colour = "black"))

```
####Plotting Rts through Trial type (it works with CleanData4!!!)
```{r}

DataNew <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "10"| Condition == "9")

DataSubset$TrialType2 = factor(DataSubset$TrialType2, levels=c("Training","Testing-Old","Testing-New"), labels=c("Training","Testing-Old","Testing-New")) 

ggplot(DataSubset, aes(x= Block, y= RT, colour= Condition, linetype = Condition)) + 
  geom_smooth(aes(colour = Condition),size = 1.0,se = TRUE, method= 'loess', formula =  y~x)+
  
  scale_linetype_manual(values = c("solid", "dotdash",
                                    "solid", "dotdash",
                                    "longdash")) +
  
  scale_color_manual(values= c("#0066CC", "#000000",
                               "#33FF00", "#33FF00", 
                                "#CC0033")) +
                               
  ggtitle("Performance by Block") +
  labs(x="Block", y="RT in ms") +
  facet_grid(~TrialType2, scales="free", space= "free_x" ) +
  theme(axis.title.y = element_text(size=12,  color="#666666")) +
  theme(axis.text = element_text(size=8)) +
  theme(plot.title = element_text(size=16, face="bold", hjust=0, color="#666666")) +
  theme(strip.text.x = element_text(size = 8, colour = "black"))

```

####Modeling master thesis Correctness pilot data for Test Condition + Block
```{r}
DataNew <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "10"|Condition == "9")

DataTesting <- subset(DataSubset, TrialType == "Testing")

Model.Ress.Corr.Testing <- glmer(RespCorr ~ Condition + Block +
                          (1|ParticipantID),
                          data=DataTesting, 
                          family= binomial)

summary(Model.Ress.Corr.Testing)

anova(Model.Ress.Corr.Testing)

summary(glht(Model.Ress.Corr.Testing, linfct = mcp(Condition = "Tukey")), test = adjusted("holm"))
```

####Modeling master thesis Correctness pilot data for Training Condition + Block
```{r}
DataNew <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "10"|Condition == "9")

DataTraining <- subset(DataSubset, TrialType == "Training")

Model.Ress.Corr.Testing <- glmer(RespCorr ~ Condition + Block +
                          (1|ParticipantID),
                          data=DataTraining, 
                          family= binomial)

summary(Model.Ress.Corr.Testing)

anova(Model.Ress.Corr.Testing)

summary(glht(Model.Ress.Corr.Testing, linfct = mcp(Condition = "Tukey")), test = adjusted("holm"))
```

####Modeling master thesis RT pilot data for Test Condition + Block
```{r}
DataNew <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "10"|Condition == "9")

DataTesting <- subset(DataSubset, TrialType == "Testing")

Model.Ress.Corr.Testing <- glmer(RT ~ Condition + Block +
                          (1|ParticipantID),
                          data=DataTesting, 
                          family= gaussian)

summary(Model.Ress.Corr.Testing)

anova(Model.Ress.Corr.Testing)

summary(glht(Model.Ress.Corr.Testing, linfct = mcp(Condition = "Tukey")), test = adjusted("holm"))
```

#Modeling master thesis RT pilot data for Training Condition + Block
```{r}
DataNew <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "10"|Condition == "9")

DataTraining <- subset(DataSubset, TrialType == "Training")

Model.Ress.Corr.Testing <- glmer(RT ~ Condition + Block +
                          (1|ParticipantID),
                          data=DataTraining, 
                          family= gaussian)

summary(Model.Ress.Corr.Testing)

anova(Model.Ress.Corr.Testing)

summary(glht(Model.Ress.Corr.Testing, linfct = mcp(Condition = "Tukey")), test = adjusted("holm"))
```