---
title: "Stekic et al."
subtitle: 'Data modeling and plotting'
output: 
  html_document:
    keep_md: true
    theme: journal
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
    code_folding: hide
---

#Introduction

The following is data analysis for Stekic, Kovic, and Nielsen (2019), where we explored the learnability of artificial languages that differed in the relationship between those labels and the objects that they describe. All files for this experiment can be found at our [GitHub Repository](https://github.com/hecticdialectic/Stekic-et-al) and further details of the experimental design can be found at our OSF Repository.

Below in two code chunks we load libraries and read in our files. 

Note that in this document all code is "folded" by default- you can unfold sections (and look at the code) by clicking on the "Code" button on the Top Right of each block.

####Loading Libraries
```{r}
library(data.table)
library(tidyverse)
library(ggthemes)
library(outliers)
library(lme4)
library(lmerTest)
library(afex)
library(kableExtra)
library(agricolae)
library(multcomp)
```

####Modeling Correctness Trainging data with Condition as fixed factor
```{r}
DataNew <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanData.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTraining <- subset(DataSubset, TrialType == "Training")

Model.Ress.Corr.Training <- glmer(RespCorr ~ Condition +
                          (1|ParticipantID),
                          data=DataTraining, 
                          family= binomial)

summary(Model.Ress.Corr.Training)

anova(Model.Ress.Corr.Training)

summary(glht(Model.Ress.Corr.Training, linfct = mcp(Condition = "Tukey")), test = adjusted("holm"))


```

####Modeling Correctness Test data with Condition as fixed factor
```{r}

DataNew <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanData.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTest <- subset(DataSubset, TrialType == "Testing")


Model.Ress.Corr.Testing <- glmer(RespCorr ~ Condition +
                          (1|ParticipantID),
                          data=DataTest, 
                          family= binomial)

summary(Model.Ress.Corr.Testing)

anova(Model.Ress.Corr.Testing)

summary(glht(Model.Ress.Corr.Testing, linfct = mcp(Condition = "Tukey")), test = adjusted("holm"))
```

####Plotting Correctness for Training
```{r}
CleanData2 <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataSubset <- subset(CleanData2, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTraining <- subset(DataSubset, TrialType == "Training")

ggplot(DataTraining, aes(x= Block, y= RespCorr, colour= Condition, linetype = Condition)) + 
  geom_smooth(aes(colour = Condition),size = 1.0,se = TRUE, method= 'loess', formula =  y~x)+
  
    scale_linetype_manual(values = c("solid", "dotdash", "dotted",
                                    "solid", "dotdash", "dotted",
                                    "solid", "dotdash", "dotted","longdash")) +
  
  scale_color_manual(values= c("#0066CC", "#000000", "#0066CC", "#0066CC",
                               "#33FF00", "#33FF00", "#33FF00", 
                               "#CC0033", "#CC0033", "#CC0033")) +
  
                               
  ggtitle("Training Performance") +
  labs(x="Block", y="Proportion of Correctness") +
  theme(axis.title.y = element_text(size=12,  color="#666666")) +
  theme(axis.text = element_text(size=8)) +
  theme(plot.title = element_text(size=16, face="bold", hjust=0, color="#666666")) +
  theme(strip.text.x = element_text(size = 8, colour = "black"))

```

####Plotting Correctness for Testing
```{r}
CleanData2 <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataSubset <- subset(CleanData2, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTesting <- subset(DataSubset, TrialType2 == "Testing-Old" | TrialType2 == "Testing-New")

ggplot(DataTesting, aes(x= Block, y= RespCorr, colour= Condition, linetype = Condition)) + 
  geom_smooth(aes(colour = Condition),size = 1.0,se = TRUE, method= 'loess', formula =  y~x)+
  
    scale_linetype_manual(values = c("solid", "dotdash", "dotted",
                                    "solid", "dotdash", "dotted",
                                    "solid", "dotdash", "dotted","longdash")) +
  
  scale_color_manual(values= c("#0066CC", "#000000", "#0066CC", "#0066CC",
                               "#33FF00", "#33FF00", "#33FF00", 
                               "#CC0033", "#CC0033", "#CC0033")) +
  
                               
  ggtitle("Test Performance") +
  labs(x="Block", y="Proportion of Correctness") +
  facet_grid(~TrialType2, scales="free", space= "free_x") +
  theme(axis.title.y = element_text(size=12,  color="#666666")) +
  theme(axis.text = element_text(size=8)) +
  theme(plot.title = element_text(size=16, face="bold", hjust=0, color="#666666")) +
  theme(strip.text.x = element_text(size = 8, colour = "black"))
```

####Modeling Correctness Training data with Block as fixed factor
```{r}
DataNew <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanData.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)
DataNew$Block <- as.factor(DataNew$Block)


DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTraining <- subset(DataSubset, TrialType == "Training")

Model.Block.Training <- glmer(RespCorr ~ Block +
                          (1|ParticipantID),
                          data=DataTraining, 
                          family= binomial)

summary(Model.Block.Training)

anova(Model.Block.Training)

summary(glht(Model.Block.Training, linfct = mcp(Block = "Tukey")), test = adjusted("holm"))
```

####Modeling Correctness Testing data with Block as fixed factor
```{r}
DataNew <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanData.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)
DataNew$Block <- as.factor(DataNew$Block)


DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTesting <- subset(DataSubset, TrialType == "Testing")

Model.Block.Testing <- glmer(RespCorr ~ Block +
                          (1|ParticipantID),
                          data=DataTesting, 
                          family= binomial)

summary(Model.Block.Testing)

anova(Model.Block.Testing)

summary(glht(Model.Block.Testing, linfct = mcp(Block = "Tukey")), test = adjusted("holm"))
```

####Plotting Correctness through Trial type (it works with CleanData4!!!)
```{r}

DataNew <- read.csv("D:/WIN/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "10"| Condition == "9")

DataSubset$TrialType2 = factor(DataSubset$TrialType2, levels=c("Training","Testing-Old","Testing-New"), labels=c("Training","Testing-Old","Testing-New")) 

ggplot(DataSubset, aes(x= Block, y= RespCorr, colour= Condition, linetype = Condition)) + 
  geom_smooth(aes(colour = Condition),size = 1.0,se = TRUE, method= 'loess', formula =  y~x)+
  
  scale_linetype_manual(values = c("solid", "dotdash",
                                    "solid", "dotdash",
                                    "longdash")) +
  
  scale_color_manual(values= c("#0066CC", "#000000",
                               "#33FF00", "#33FF00", 
                                "#CC0033")) +
                               
  ggtitle("Performance by Block") +
  labs(x="Block", y="Proportion of Correctness") +
  facet_grid(~TrialType2, scales="free", space= "free_x" ) +
  theme(axis.title.y = element_text(size=12,  color="#666666")) +
  theme(axis.text = element_text(size=8)) +
  theme(plot.title = element_text(size=16, face="bold", hjust=0, color="#666666")) +
  theme(strip.text.x = element_text(size = 8, colour = "black"))

```

####Modeling Corectness for Stimuli Sets / Testing
```{r}
DataNew <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)
DataNew$Block <- as.factor(DataNew$Block)
DataNew$Set <- as.factor(DataNew$Set)


DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTesting <- subset(DataSubset, TrialType == "Testing")

Model.Set.Testing <- glmer(RespCorr ~ Set +
                          (1|ParticipantID),
                          data=DataTesting, 
                          family= binomial)

summary(Model.Set.Testing)

anova(Model.Set.Testing)

summary(glht(Model.Set.Testing, linfct = mcp(Set = "Tukey")), test = adjusted("holm"))
```

####Modeling Corectness for Stimuli Sets / Training
```{r}
DataNew <- read.csv("C:/Users/775/Documents/GitHub/Stekic-et-al/Data/CleanData4.csv")

DataNew$ParticipantID <- as.factor(DataNew$ParticipantID)
DataNew$Condition <- as.factor(DataNew$Condition)
DataNew$Block <- as.factor(DataNew$Block)
DataNew$Set <- as.factor(DataNew$Set)


DataSubset <- subset(DataNew, Condition == "1"|Condition == "2"|Condition == "3A"|Condition == "4"|Condition == "10"| Condition == "5"| 
                       Condition == "6A"|Condition == "7"|Condition == "8"|Condition == "9")

DataTraining <- subset(DataSubset, TrialType == "Training")

Model.Set.Training <- glmer(RespCorr ~ Set +
                          (1|ParticipantID),
                          data=DataTraining, 
                          family= binomial)

summary(Model.Set.Training)

anova(Model.Set.Training)

summary(glht(Model.Set.Training, linfct = mcp(Set = "Tukey")), test = adjusted("holm"))
```