---
title: "Ketrin Experiment Generator"
author: "Alan Nielsen"
date: "September 2, 2017"
output: html_document
---

In this document we will be taking a look at creating stimlists for Stekic, Nielsen, & Kovic

This experiment will be an extension of the protocol use by Lupyan et al. (2007)

#Images

Lupyan et al. used at minimum 24 aliens- 12 of each type.

Here, we will use a total of 40 "microbes" (bouba kiki shapes), of which each experimental participant will see a set of 24.

These stimuli will be drawn from a set of stimuli from Yardy (2010)- in his thesis, Yardy made a very large set of stimuli that were created from the same image seed (of which we have 144 total) but then varied in their degree of pointiness-curviness on a scale of 1 to 100. However, participants basically didn't differentiate curviness past about 30 on that scale, so we won't either.

From this set of stimuli, we will select a total of 20 - which will yield 40 overall images (20 curvy, 20 spiky). Lets do so randomly with a tiny bit of R wizardry.

We can do this pretty easily- we simply create a vector that is all of the numbers 1 to 144, then sample from it 40 times without replacement (Which picks 20 numbers between 1 and 144)

Note- we do this here by setting a seed for the random number generator so we get the same thing every time- this means that the stimuli we actually pick will be the same every time- so once we pick them you won't look at the stimlist, run this again, and say "why the hell are the stims a different number"

##Image Selection

```{r Choosing Images}
set.seed(11120)
list <- 1:144
chosen <- sample(list, 20, replace = FALSE)
chosen
```

With these 20 chosen seeds, we'll be able to generate our 40 total stims

But how do we choose what range of "curviness" to use? One possibility is that this is something we can also manipulate in the experimental design- how good of an exemplar each individual token is of its category.

For that purpose, we're going to select our jagged and curvy images from these seeds in 4 subsets

Subset 1: Jagged = 0, Curvy = 30
Subset 2: Jagged = 0, Curvy = 20
Subset 3: Jagged = 10, Curvy = 30
Subset 4: Jagged = 10, Curvy = 20

(Note that we can reconsider these selections fairly easily)

So lets do that with some more quick R

Here we first scramble our list of chosen stimuli (which we can do with just the **sample()** command)
Then we split it into 4 equally sized lists of 5 (which we do with the split command)
```{r Choosing Images II}
chosen <- sample(chosen)
ChosenSplit <- split(chosen, rep(1:4, each = 5))

Chosen1 <- ChosenSplit$'1'
Chosen2 <- ChosenSplit$'2'
Chosen3 <- ChosenSplit$'3'
Chosen4 <- ChosenSplit$'4'

ChosenSplit
```

So now we can write a little script that deletes all of the files that we don't want.

To do this we need to take our current lists (which are just file numbers) and convert them into file names that we want to select

First, we'll double each list (simply by concatenating it with itself)
Then we'll create some cheeky lists 
  The first of these (a set of lists) just makes vectors of lists of numbers - the same numbers- this will create a column   that simply lists the Image Subtype
  
  The second of these is just a list of 5Cs and 5Js
  
  The third of these (a set of lists) gives the actual "values" of the files to be selected- aka what       degree of curviness between 0 and 100

```{r Choosing Images III}
Chosen1 <- c(Chosen1, Chosen1)
Chosen2 <- c(Chosen2, Chosen2)
Chosen3 <- c(Chosen3, Chosen3)
Chosen4 <- c(Chosen4, Chosen4)
######
Chosen1Num <- rep(1,10)
Chosen2Num <- rep(2,10)
Chosen3Num <- rep(3,10)
Chosen4Num <- rep(4,10)
######
BalanceList <- c(rep("J", 5), rep("C",5))
######
Chosen1JC <- c(rep(0,5), rep(30,5))
Chosen2JC <- c(rep(0,5), rep(20,5))
Chosen3JC <- c(rep(10,5), rep(30,5))
Chosen4JC <- c(rep(10,5), rep(20,5))

```

This gives us the basic pieces we need for our filenames- both the current filesnames (which allows them to be selected), and the eventual full filenames

So now all we need to do is put that together
Which we're going to do by assembling what we have into a dataframe- fortunately this is *really* easy to do with the **cbind()** (column bind) and **rbind()** (rowbind) commands

First we'll do the column binding and take a look at what it gives us
```{r C-binding}

Chosen1<- cbind(Chosen1, Chosen1Num, BalanceList, Chosen1JC)
Chosen2<- cbind(Chosen2, Chosen2Num, BalanceList, Chosen2JC)
Chosen3<- cbind(Chosen3, Chosen3Num, BalanceList, Chosen3JC)
Chosen4<- cbind(Chosen4, Chosen4Num, BalanceList, Chosen4JC)

head(Chosen1)

```

Now we'll use rbind() to simply stick these onto each other, and at the same time turn them into a proper dataframe (rather than a vector of vectors) (note, this also gets rid of the quote marks around the entries)
Then we'll quickly rename the columns to make them a bit more informative


```{r R-binding}
ImageStims <- as.data.frame(rbind(Chosen1, Chosen2, Chosen3, Chosen4))
colnames(ImageStims) <-c("SeedNum", "SubType", "Shape", "Curviness")
head(ImageStims)
```

Now we can produce our filenames

The filenames as they are are just SeedNum-Curviness.bmp (e.g. '57-0.jpg'). So to create that from our data we just need to paste the columns SeedNum and Curviness together

Then for the filename we eventually want, we paste Seednum-Shape-Curviness-SubType

```{r Filename Generator}

ImageStims$Original <- with(ImageStims, paste(SeedNum, Curviness, sep = '-'))
ImageStims$NewName <- with(ImageStims, paste(SeedNum, Shape, Curviness, SubType, sep = '-'))

head(ImageStims)

```

So now we want to delete all files *other than* the ones we want

First we'll generate a list of all files in the directory (this will be a *very* long vector- 14,400 entries long)

Then we make another vector which is just the files we want to keep- which we extract from ImageStims$Original, then paste .bmp onto

```{r File Lister}
filelist <- list.files('F:/Experiments/Collaborations/Stekic et al/Figures/Figures/') ## we will use the actual directory when we do this for real
head(filelist)

FilesToKeep <- with(ImageStims, paste(Original, ".bmp", sep = ''))
head(FilesToKeep)
```

So now you can see that we have two vectors that have their strings formatted in the same way- one is much longer than the other.

So the first thing we're going to do is cut down the long list to a list of *only* the files that we don't want to keep - Fortunately this is really easy to do using **setdiff()**

Then we simply use **file.remove()** on the new vector to remove the files that we don't want

```{r File Deleted, warning = FALSE, message = FALSE}
setwd('F:/Experiments/Collaborations/Stekic et al/Figures/Figures/')
FilesToDelete <- setdiff(filelist, FilesToKeep)
head(FilesToDelete)

file.remove(FilesToDelete)
```
So now the last thign we need to do is rename some files.
We can do this with **file.rename()**, which just like file.remove() can take a vector, but in this case can take 2 vectors- a *from* vector and a *to* vector

Fortunately we already have our from and to vectors- they are part of our ImageList dataframe

Here is what I tested on
```{r Test file.rename}
setwd('F:/Experiments/Collaborations/Stekic et al/Figures/Test/')
oldnames <- list.files()
newnames <- paste("renamed", oldnames, sep = "-")

oldnames
newnames
file.rename(oldnames, newnames)

list.files()
```

and here is the real code we will run

```{r File Renamer}
setwd('F:/Experiments/Collaborations/Stekic et al/Figures/Figures/')
OriginalNames <- ImageStims$Original
OriginalNames <- paste(OriginalNames, ".bmp", sep = '')
NewNames <- ImageStims$NewName
NewNames <- paste(NewNames, ".bmp", sep= '')
file.rename(OriginalNames, NewNames)

setwd('F:/Experiments/Collaborations/Stekic et al/Figures/')
write.csv(ImageStims, "ChosenImages.csv")

```


So that's it for this File - we've:

1) Selected 20 Image Seeds from the 144 total

2) Selected both a Curvy and a Jagged image from those image seeds, according to 4 image subtypes (1: Jagged = 0, Curvy = 30; 2: Jagged = 0, Curvy = 20; 3: Jagged = 10, Curvy = 30; 4: Jagged = 10, Curvy = 20)

3) Deleted all files other than those we want (from 8080 files to 40)

4) Renamed those files to more informative names that can be used in the Experiment Files

5) Exported the ImageStims file as a .csv that can be loaded into subsequent RMDs which generate experimental trial structure.













